---
title: "testadd package"
output: github_document
---

Starter code for a package with the function `add()`. 
Note that this readme.md is generated by the readme.rmd file.

Readiness test:

- Create a new branch "add_test" (either locally or remotely)
- On this new branch, make the following changes locally:

 1. Edit the function add() such that it returns an error if x or y are not numeric
 2. Add a testing set up (as per demo on second last slide in ppt robust functions testing)
 3. Add a test for one of the following tasks:
 
	- Verify that the function add gives an error when x or y are character strings or logicals (TRUE or FALSE), OR
	- Verify that the function add returns the correct answer for some simple calculations, i.e. for x=1, y=2. 
	
 4. Add an R script to run the test and check that the output is as expected, or use this readme.RMD file for that. 
- Commit and push these local changes.
- Issue a pull request to merge your updated branch into your main branch. 
- Accept the pull request and then delete the add_test branch on GitHub. 
(You also can/should delete the add_test branch in your local repo but we won't be able to check whether you do this!) 
- Understand that in a "real-world" situation it would usually not be a good idea to accept your own pull request.  The purpose
of a PR (in a repo you have access to) is usually to give your collaborators a chance to look at your work and agree to the merge...

Some code is added below that may be helpful

```{r}
library(devtools)
load_all("../test3") # with your name added
```

```{r}
add(1, 2)
```

